---
title: "Meta-Regression Analysis of Tobacco Smoking as a Risk Factor for Lung Cancer"
author: "Joshua Edefo"
email: "edefojoshu2000@yahoo.com"
date: "2024-01-16"
output: github_document
---
This meta-regression analyses three hypothetical studies on tobacco smoking as a risk factor for lung cancer. All studies report a moderate positive association (ZCOR: 0.29–0.45), with confidence intervals excluding zero, indicating statistical significance. "Lieu et al" contributes the most (46.8%), while "Edefo et al" contributes the least (20.8%). The pooled effect size is 0.3606 (95% CI: [0.2266, 0.4947], p < 0.0001), confirming a significant association. With no substantial heterogeneity, this analysis provides strong evidence that tobacco smoking increases lung cancer risk consistently across studies.

Libraries 
```{r a, message=FALSE}
library(usethis)
library(meta)
library(readxl)
```

Meta Regression

```{r b}
## Set directory

setwd("C:\\Users\\joe62\\OneDrive - Aberystwyth University\\Apps\\Desktop\\Destop Folder")

## Importing the data
data <- read_excel("metasamples(2).xlsx")
View(data)
head(data)
 
## Conduct meta-analysis using Standardized Regression Coefficients
Metaregression <- metagen(TE =data$beta, seTE = data$se_beta, 
                  data = data,studlab = Author, fixed = TRUE, random = TRUE,
                  sm = "ZC OR")  # "ZCOR" for Fisher's z-transformed correlation

## Summary of meta-analysis
summary(Metaregression)

## Generate a forest plot
forest(Metaregression, leftcols = c("studlab", "TE", "seTE"))

##  The ovearll  effect size is 0.3606 (95% CI: [0.2266, 0.4947], p < 0.0001, meaning tobacco smoking ia a risk factor for developing lung cancer
```

Session information

```{r c}

sessionInfo()

```

